Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-06-21 paper/v2/paper-edited.tex
more spelling corrections + acknowledgment fix

We use graph dominators~\cite{tarjan-dominance} as a cheap approximation for removing many nodes and edges in the PGIR that are never on any \emph{simple} (loop free) path between the start and end nodes.
In the PGIR, a node $x$ dominates a node $y$ if $x$ appears on every path leading from the start node to $y$. Similarly, a node $x$ post-dominates a node $y$ in the PGIR if $x$ appears on every path from $y$ to the end node.
We can safely remove nodes and edges in the PGIR when any of the following conditions hold, where $x$, $x'$ and $y$, $y'$ refer to PGIR nodes that are shadows of the same topology location.
\begin{itemize}
\setlength{\itemsep}{1pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\item Remove $x$ if it is not reachable from the start node
\item Remove $x$ if it can not reach the end node
\item Remove $x$ if it is (post-)dominated by some $x'$
\item Remove edge ($x$, $y$) if $y$ is post-dominated by some $x'$
\item Remove edge ($x$, $y$) if $x$ is dominated by some $y'$
\end{itemize}
For example, node $(W,1,1)$ in Figure~\ref{fig:example-compilation} is removed since it is never on a simple path to the end node, because the path must always go through node $(W,-,4)$. That is, node $(W,-,4)$ post-dominates node $(W,1,1)$ and both are shadows of topology location $W$.
Similarly, the edge from $(C,3,2)$ to $(D,-,2)$ is removed since node $(C,-,2)$ post-dominates $(D,-,2)$ and is a shadow of the same topology location $C$.

@@

Searching for precise regret-free preferences in general is hard, and clearly enumerating all possible combinations of failures and preference orderings is intractable. We thus adopt a conservative analysis that we found to be effective and efficient in practice. The idea is to $i)$ search for regret-free preferences by comparing the set of paths available after accepting advertisments in two different PGIR shadows $N_1$ and $N_2$ of topology node $N$, and $ii)$ refine the comparison when necessary by considering where the announcements must have traversed before arriving at $N_1$ or $N_2$.

@@

Instead, we adopt the following simple strategy: $i)$ pick a random origin-to-aggregation path in the PGIR, $ii)$ remove all similar edges in the PGIR for the topological edges chosen, and $iii)$ repeat until no such path exists.
Because each path chosen is both policy compliant and edge disjoint (due to ii), the number of paths that we are able to remove lower bounds the number of failures required to disconnect the prefix from its aggregate, subject to the policy constraints.

@@

\ryan{TODO: add acknowledgements}
We thank R. Aditya, George Chen, and Lihua Yuan for feedback on this work and the SIGCOMM reviewers for comments on the paper.

>>>>

We use graph dominators~\cite{tarjan-dominance} as a cheap approximation for removing many nodes and edges in the PGIR that are never on any \emph{simple} (loop free) path between the start and end nodes.
In the PGIR, a node $x$ dominates a node $y$ if $x$ appears on every path leading from the start node to $y$. Similarly, a node $x$ post-dominates a node $y$ in the PGIR if $x$ appears on every path from $y$ to the end node.
We can safely remove nodes and edges in the PGIR when any of the following conditions hold, where $x$, $x'$ and $y$, $y'$ refer to PGIR nodes that are shadows of the same topology location.
\begin{itemize}
\setlength{\itemsep}{1pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\item Remove $x$ if it is not reachable from the start node
\item Remove $x$ if it can not reach the end node
\item Remove $x$ if it is (post-)dominated by some $x'$
\item Remove edge ($x$, $y$) if $y$ is post-dominated by some $x'$
\item Remove edge ($x$, $y$) if $x$ is dominated by some $y'$
\end{itemize}
For example, node $(W,1,1)$ in Figure~\ref{fig:example-compilation} is removed because every path to the end node must always go through node $(W,-,4)$. That is, node $(W,-,4)$ post-dominates node $(W,1,1)$ and both are shadows of topology location $W$.
Similarly, the edge from $(C,3,2)$ to $(D,-,2)$ is removed since node $(C,-,2)$ post-dominates $(D,-,2)$ and is a shadow of $C$.

@@

Searching for precise regret-free preferences in general is hard, and clearly enumerating all possible combinations of failures and preference orderings is intractable. We thus adopt a conservative analysis that we found to be effective and efficient in practice. The idea is to $i)$ search for regret-free preferences by comparing the set of paths available after accepting advertisements in two different PGIR shadows $N_1$ and $N_2$ of topology node $N$, and $ii)$ refine the comparison when necessary by considering where the announcements must have traversed before arriving at $N_1$ or $N_2$.

@@

Instead, we adopt the following simple strategy: $i)$ pick a random path in the PGIR between the prefix origin and aggregation point, $ii)$ remove all similar edges in the PGIR for each topological edges along the chosen path, and $iii)$ repeat until no such path exists.
Because each path chosen is both policy compliant and edge disjoint (due to ii), the number of paths that we are able to remove lower bounds the number of failures required to disconnect the prefix from its aggregate, subject to the policy constraints.

@@

We thank R. Aditya, George Chen, and Lihua Yuan for feedback on this work and the SIGCOMM reviewers for comments on the paper. This work is supported in part by the National Science Foundation award CNS-1161595.
